---
title: "DataExploration"
author: "Jay and Jessica"
date: "5/8/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Let's try and get some basic stats first

Load the packages you will need using library()
```{r}
#install.packages("tidyverse")
library(tidyverse)
```

Read your csv dataset into a tibble dataframe on R
```{r}
#install.packages("tibble")
library(tibble)
fsb = read.csv("SexBehavior.csv")
as_tibble(fsb)
```

What are the names of the columns?
```{r}
colnames(fsb, do.NULL = TRUE, prefix = "col")
```

How many rows of data do you have? 
```{r}
rownames(fsb, do.NULL = TRUE, prefix = "row")

##Ans:107
```

How many unique trials had sex behavior in them? 
```{r}
sbd = read.csv("Sexual Behavior Data Sheets.csv")
as_tibble(sbd)
names(sbd)[names(sbd) == 'X.0.1..court.copul.presence'] <- 'presence'

library(dplyr)
sexbpres = sbd %>%
  filter(presence == 1)
rownames(sexbpres, do.NULL = TRUE, prefix = "row")

##Ans:31
```

How many unique bouts of behavior exist in the data set? 
```{r}
list(fsb$bout_num)

##Ans:64
```

##Advanced stuff below!!!

Currently your main data sheet does not have the date in it. Read in your "Sexual Behavior Data Sheet" csv into a tibble dataframe, which does have the date.
```{r}
sbd = read.csv("Sexual Behavior Data Sheets.csv")
as_tibble(sbd)
```

Dates usually are default read in as characters and are not interpreted as dates. Use the lubridate package to "parse" your date column -- change it from a character to a date
```{r}
#install.packages("lubridate")
library(lubridate)

newdate = sbd %>%
  mutate(date = ymd(sbd$date))

as_tibble(newdate)
```

Use the trial_num column in both of your data frames to join the two together. Hint: you'll need to use some sort of "join" function from dplyr package
```{r}
m.trial.date = merge(newdate$trial_num, newdate$date, by="date")
as_tibble(m.trial.date)
```

What date had the highest number of bouts?
```{r}
max(fsb$bout_num)
```







