---
title: "DataExploration"
author: "Jay and Jessica"
date: "5/8/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Let's try and get some basic stats first

Load the packages you will need using library()
```{r}

```

Read your csv dataset into a tibble dataframe on R
```{r}

```

What are the names of the columns?
```{r}

```

How many rows of data do you have? 
```{r}

```

How many unique trials had sex behavior in them? 
```{r}

```

How many unique bouts of behavior exist in the data set? 
```{r}

```

##Advanced stuff below!!!

Currently your main data sheet does not have the date in it. Read in your "Sexual Behavior Data Sheet" csv into a tibble dataframe, which does have the date.
```{r}

```

Dates usually are default read in as characters and are not interpreted as dates. Use the lubridate package to "parse" your date column -- change it from a character to a date
```{r}

```

Use the trial_num column in both of your data frames to join the two together. Hint: you'll need to use some sort of "join" function from dplyr package
```{r}

```

What date had the highest number of bouts?
```{r}

```







