---
title: "SexBehaviorAnalysis"
author: "Jessica Lecorchick & Jay Falk"
date: "7/3/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load necessary packages 
```{r, message = FALSE}
library(tidyverse)
```

Load all data sets here
```{r, message = FALSE}
fsb <- read_csv("SexBehavior.csv")
data <- read_csv("Sexual Behavior Data Sheets.csv")
tt <- read_csv("trialtype.obsrate.csv")
view(fsb)
```



#### First let's look at who males decided to copulate/court first within each trial 

Which mount type was first courted/copulated within each trial? (M/F)
```{r}
m.f <- fsb %>% 
  filter(trial_type == "M/F")

m.f
```
Trials: 10 in total
Firsts:
15: copul, F, L
23: copul, F, L
29: copul, F, R
36: copul, F, R
38: copul, F, L
43: copul, F, R
70: court, F, L
74: copul, F, L
83: court, F, L
93: copul, F, L

Which mount type was first courted/copulated within each trial? (F/MLF)
```{r}
f.mlf <- fsb %>%
  filter(trial_type == "F/MLF")

f.mlf
```
Trials: 14 in total (12 usable, 2 non-usable)
Firsts:
16: copul, F, L
37: copul, F, R
47: court, F, L
54: copul, F, R
57: copul, F, L
63: copul, F, L
72: court, F, L
75: court, F, R
78: UNSPECIFIED
81: copul, F, R
84: copul, F, R
87: court, F, L
91: UNSPECIFIED
94: copul, F, R

Which mount type was first courted/copulated within each trial? (M/MLF)
```{r}

```

#### Now instead of looking at the first decision within each trial, lets look at the first decision within each bout

Which mount type was first courted/copulated within each bout? (M/F)
```{r}

```

Which mount type was first courted/copulated within each bout? (F/MLF)
```{r}

```

Which mount type was first courted/copulated within each bout? (M/MLF)
```{r}

```

#### Now let's look overall. How many instances of courtship/copulation at each side? 

Which mount type was first courted/copulated within each bout? (M/F)