---
title: "SexBehaviorAnalysis"
author: "Jessica Lecorchick & Jay Falk"
date: "7/3/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load necessary packages 
```{r, message = FALSE}
library(tidyverse)
```

Load all data sets here
```{r, message = FALSE}

```


#### First let's look at who males decided to copulate/court first within each trial 

Which mount type was first courted/copulated within each trial? (M/F)
```{r}

```

Which mount type was first courted/copulated within each trial? 
```{r}

```

Which mount type was first courted/copulated within each trial? (M/MLF)
```{r}

```

#### Now instead of looking at the first decision within each trial, lets look at the first decision within each bout

Which mount type was first courted/copulated within each bout? (M/F)
```{r}

```

Which mount type was first courted/copulated within each bout? (F/MLF)
```{r}

```

Which mount type was first courted/copulated within each bout? (M/MLF)
```{r}

```

#### Now let's look overall. How many instances of courtship/copulation at each side? 

Which mount type was first courted/copulated within each bout? (M/F)