---
title: "SexBehaviorAnalysis"
author: "Jessica Lecorchick & Jay Falk"
date: "7/3/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load necessary packages 
```{r, message = FALSE}
library(tidyverse)
```

Load all data sets here
```{r, message = FALSE}
fsb <- read_csv("SexBehavior.csv")
data <- read_csv("Sexual Behavior Data Sheets.csv")
tt <- read_csv("trialtype.obsrate.csv")
view(fsb)
```



#### First let's look at who males decided to copulate/court first within each trial 

Which mount type was first courted/copulated within each trial? (M/F)
```{r}
m.f <- fsb %>% 
  filter(trial_type == "M/F")

m.f
```
Trials: 10 in total
Firsts:
15: copul, F, L
23: copul, F, L
29: copul, F, R
36: copul, F, R
38: copul, F, L
43: copul, F, R
70: court, F, L
74: copul, F, L
83: court, F, L
93: copul, F, L
c/c: 2 courts, 8 copuls
type: 10 F, 0 M
side:  7 L, 3 R

Which mount type was first courted/copulated within each trial? (F/MLF)
```{r}
f.mlf <- fsb %>%
  filter(trial_type == "F/MLF")

f.mlf
```
Trials: 14 in total (12 usable, 2 non-usable)
Firsts:
16: copul, F, L
37: copul, F, R
47: court, F, L
54: copul, F, R
57: copul, F, L
63: copul, F, L
72: court, F, L
75: court, F, R
78: UNSPECIFIED
81: copul, F, R
84: copul, F, R
87: court, F, L
91: UNSPECIFIED
94: copul, F, R
c/c: 4 courts, 8 copuls
type: 12 F, 0 MLF
side: 6 L, 6 R

Which mount type was first courted/copulated within each trial? (M/MLF)
```{r}
m.mlf <- fsb %>%
  filter(trial_type == "M/MLF")

m.mlf
```
Trials: 7 trials in total
Firsts:
31: court, MLF, R
58: copul, M, R
67: copul, MLF, L
76: copul, MLF, R
79: court, M, R
82: copul, M, R 
98: copul, MLF, L
c/c: 2 courts, 5 copuls
type: 4 MLF, 3 M
sideL 2 L, 5 R

#### Now instead of looking at the first decision within each trial, lets look at the first decision within each bout

Which mount type was first courted/copulated within each bout? (M/F)
```{r}
m.f <- fsb %>% 
  filter(trial_type == "M/F")

m.f
```
Total bouts: 20 in total
Firsts: 
15:1: copul	L	F
23:1: copul	L	F
23:2: court	L	F
29:1: copul	R	F
29:2: copul	R	F
29:3: copul	R	F
29:4: copul	R	F
29:5: copul	R	F
36:1: copul	R	F
36:2: copul	R	F
36:3: copul	R	F
38:1: copul	L	F
43:1: copul	R	F
70:1: court	L	F
70:2: court	L	F
74:1: copul	L	F
83:1: court	L	F
93:1: copul	L	F
93:2: copul	L	F
93:3: copul	L	F
c/c: 4 courts, 16 copuls
type: 20 F, 0 M
side: 11 L, 9 R

Which mount type was first courted/copulated within each bout? (F/MLF)
```{r}
f.mlf <- fsb %>%
  filter(trial_type == "F/MLF")

f.mlf
```
Total bouts:
Firsts:
16:1: copul	L	F
37:1: copul	L	F
37:2: UNSPECIFIED
47:1: court	L	F
47:2: court	L	F
54:1: copul	R	F 
54:2: copul	R	F
54:3: copul	L	MLF
54:4: copul	R	F
57:1: copul	L	F
63:1: copul	L	F
72:1: court	L	F
75:1: court	R	F
75:2: court	R	F
75:3: copul	R	F
75:4: court	R	F
75:5: copul	R	F
75:6: court	L	MLF
75:7: copul	R	F
78:1: UNSPECIFIED
78:2: UNSPECIFIED
81:1: copul	R	F
84:1:
84:2:
84:3:
84:4:
84:5:

Which mount type was first courted/copulated within each bout? (M/MLF)
```{r}

```

#### Now let's look overall. How many instances of courtship/copulation at each side? 
