---
title: "SexBehaviorAnalysis"
author: "Jessica Lecorchick & Jay Falk"
date: "7/3/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load necessary packages 
```{r, message = FALSE}
library(tidyverse)
```

Load all data sets here
```{r, message = FALSE}
fsb <- read_csv("SexBehavior.csv")
data <- read_csv("Sexual Behavior Data Sheets.csv")
tt <- read_csv("trialtype.obsrate.csv")
#view(fsb)

#JJF: It's always good practice to put some commentary on what each of these datasets are. Treat the markdown a little like you're explaining to someone who doesn't know your work what each command does. It'll also help to name your "data" dataset something different. 
```


It'll make this easier if we have the actual mount types that the birds chose rather than just L versus R. Jessica already has this information in the "data" dataset so this should be pretty easy. 
```{r}
fsb
data

#joins are a little easier when you only have the data you're interested in combining, so I'm only selecting the mount at each side and the trial number
joindata <- data %>% select(trial_num, L, R)

#join statements are sooooo useful! Run this line and you'll see that it's jused "trial num" in both the joindata and fsb dataframes to add L and R columns to your fsb dataframe
fsbjoin <- fsb %>% left_join(joindata, by = "trial_num")

#I've made a new column that uses sideLR to get the actual mount choice. If sideLR is L, mountchoice put whatever is in the L column. If it's an R, it takes what's in the R column. If it's neither, it puts an NA. Make sure what you have in sideLR is either an L or an R or else you'll get lots of missing data.  
fsbLF <- fsbjoin %>% 
  mutate(mountchoice = if_else(sideLR == "L", L, 
                               if_else(sideLR == "R", R, NULL)))
fsbLF
```


#### First let's look at who males decided to copulate/court first within each trial 

Which mount type was first courted/copulated within each trial? (M/F)
```{r}
m.f <- fsb %>% 
  filter(trial_type == "M/F")

m.f

#The way you've done this is fine, but using the arrange and distinct functions will probably help here!
```
Trials: 10 in total
Firsts:
15: copul, F, L
23: copul, F, L
29: copul, F, R
36: copul, F, R
38: copul, F, L
43: copul, F, R
70: court, F, L
74: copul, F, L
83: court, F, L
93: copul, F, L
c/c: 2 courts, 8 copuls
type: 10 F, 0 M
side:  7 L, 3 R

Which mount type was first courted/copulated within each trial? (F/MLF)
```{r}
f.mlf <- fsb %>%
  filter(trial_type == "F/MLF")

f.mlf
```
Trials: 14 in total (12 usable, 2 non-usable)
Firsts:
16: copul, F, L
37: copul, F, R
47: court, F, L
54: copul, F, R
57: copul, F, L
63: copul, F, L
72: court, F, L
75: court, F, R
78: UNSPECIFIED
81: copul, F, R
84: copul, F, R
87: court, F, L
91: UNSPECIFIED
94: copul, F, R
c/c: 4 courts, 8 copuls
type: 12 F, 0 MLF
side: 6 L, 6 R

Which mount type was first courted/copulated within each trial? (M/MLF)
```{r}
m.mlf <- fsb %>%
  filter(trial_type == "M/MLF")

m.mlf
```
Trials: 7 trials in total
Firsts:
31: court, MLF, R
58: copul, M, R
67: copul, MLF, L
76: copul, MLF, R
79: court, M, R
82: copul, M, R 
98: copul, MLF, L
c/c: 2 courts, 5 copuls
type: 4 MLF, 3 M
sideL 2 L, 5 R

#### Now instead of looking at the first decision within each trial, lets look at the first decision within each bout

Which mount type was first courted/copulated within each bout? (M/F)
```{r}
m.f <- fsb %>% 
  filter(trial_type == "M/F")

m.f
```
Total bouts: 20 in total
Firsts: 
15:1: copul	L	F
23:1: copul	L	F
23:2: court	L	F
29:1: copul	R	F
29:2: copul	R	F
29:3: copul	R	F
29:4: copul	R	F
29:5: copul	R	F
36:1: copul	R	F
36:2: copul	R	F
36:3: copul	R	F
38:1: copul	L	F
43:1: copul	R	F
70:1: court	L	F
70:2: court	L	F
74:1: copul	L	F
83:1: court	L	F
93:1: copul	L	F
93:2: copul	L	F
93:3: copul	L	F
c/c: 4 courts, 16 copuls
type: 20 F, 0 M
side: 11 L, 9 R

Which mount type was first courted/copulated within each bout? (F/MLF)
```{r}
f.mlf <- fsb %>%
  filter(trial_type == "F/MLF")

f.mlf
```
Total bouts: 35 bouts in total (31 usable, 4 non usable)
Firsts:
16:1: copul	L	F
37:1: copul	L	F
37:2: UNSPECIFIED
47:1: court	L	F
47:2: court	L	F
54:1: copul	R	F 
54:2: copul	R	F
54:3: copul	L	MLF
54:4: copul	R	F
57:1: copul	L	F
63:1: copul	L	F
72:1: court	L	F
75:1: court	R	F
75:2: court	R	F
75:3: copul	R	F
75:4: court	R	F
75:5: copul	R	F
75:6: court	L	MLF
75:7: copul	R	F
78:1: UNSPECIFIED
78:2: UNSPECIFIED
81:1: copul	R	F
84:1: copul	R	F
84:2: copul	R	F
84:3: copul	R	F
84:4: court	R	F
84:5: copul	R	F
87:1: court	L	F
91:1: UNSPECIFIED
94:1: copul	R	F
94:2: copul	R	F
94:3: copul	R	F
94:4: copul	R	F
94:5: court R F
94:6: copul L MLF
c/c: 10 courts, 21 copuls
type: 28 F, 3 MLF
side: 11 L, 20 R

Which mount type was first courted/copulated within each bout? (M/MLF)
```{r}
m.mlf <- fsb %>%
  filter(trial_type == "M/MLF")

m.mlf
```
Total bouts: 23 total bouts
Firsts: 
31:1: court	R	MLF
31:2: copul	L	M
31:3: copul	L	M
31:4: copul	L	M
31:5: copul	L	M
58:1: copul	R	M
67:1: copul	L	MLF
67:2: copul	R	M
67:3: copul	R	M
67:4: copul	L	MLF
67:5: copul	R	M
67:6: copul	R	M
67:7: copul	R	M
76:1: copul	R	MLF
79:1: court	R	M
79:2: court	L	MLF
79:3: copul	L	MLF
79:4: copul	R	M
82:1: copul	R	M
82:2: copul	R	M
98:1: copul	L	MLF
98:2: copul	L	MLF
98:3: copul	L	MLF 
c/c: 3 courts, 20 copuls
type: 14 M, 9 MLF
side: 11 L, 12 R

#### Now let's look overall. How many instances of courtship/copulation at each side? 

The left side (i did sides just to ensure randomness)
```{r}
l.copul <- fsb %>%
  filter(sideLR == "L") %>%
  filter(court.copul == "copul")
nrow(l.copul) #23
l.copul

l.court <- fsb %>%
  filter(sideLR == "L") %>%
  filter(court.copul == "court")
nrow(l.court) #16
l.court

#JJF: Is L versus R meaningful here? You probably will need to join your "data" tibble to fsb
```

The right side
```{r}
r.copul <- fsb %>%
  filter(sideLR == "R") %>%
  filter(court.copul == "copul")
nrow(r.copul) #36
r.copul

r.court <- fsb %>%
  filter(sideLR == "R") %>%
  filter(court.copul == "court")
nrow(r.court) #18
r.court
```

Male
```{r}
male.court <- fsbLF %>% 
  filter(mountchoice == "M") %>%
  filter(court.copul == "court")
nrow(male.court)
male.court #8 

male.copul <- fsbLF %>% 
  filter(mountchoice == "M") %>%
  filter(court.copul == "copul")
nrow(male.copul)
male.copul #13
```

Female
```{r}
female.court <- fsbLF %>% 
  filter(mountchoice == "F") %>%
  filter(court.copul == "court")
nrow(female.court)
female.court #23 

female.copul <- fsbLF %>% 
  filter(mountchoice == "F") %>%
  filter(court.copul == "copul")
nrow(female.copul)
female.copul #38
```

MLF
```{r}
mlf.court <- fsbLF %>% 
  filter(mountchoice == "MLF") %>%
  filter(court.copul == "court")
nrow(mlf.court)
mlf.court #3

mlf.copul <- fsbLF %>% 
  filter(mountchoice == "MLF") %>%
  filter(court.copul == "copul")
nrow(male.copul)
mlf.copul #13
```
OVERALL:
Male Court: 8 
Male Copul: 13
Male Total: 21
Female Court: 23
Female Copul: 38
Female Total: 61
MLF Court: 3
MLF Copul: 13
MLF Total: 16

#### Now let's look at each trial type overall.

M/F Male
```{r}
m.f.court.m <-fsbLF %>%
  filter(trial_type == "M/F") %>%
  filter(mountchoice == "M") %>%
  filter(court.copul == "court")
nrow(m.f.court.m) #2
m.f.court.m

m.f.copul.m <-fsbLF %>%
  filter(trial_type == "M/F") %>%
  filter(mountchoice == "M") %>%
  filter(court.copul == "copul")
nrow(m.f.copul.m) #0
m.f.copul.m 

#total for males in M/F: 2
```
M/F Female
```{r}
m.f.court.f <-fsbLF %>%
  filter(trial_type == "M/F") %>%
  filter(mountchoice == "F") %>%
  filter(court.copul == "court")
nrow(m.f.court.f) #6
m.f.court.f

m.f.copul.f <-fsbLF %>%
  filter(trial_type == "M/F") %>%
  filter(mountchoice == "F") %>%
  filter(court.copul == "copul")
nrow(m.f.copul.f) #19
m.f.copul.f 

#total for females in M/F: 25
```
F/MLF Female
```{r}
f.mlf.court.f <-fsbLF %>%
  filter(trial_type == "F/MLF") %>%
  filter(mountchoice == "F") %>%
  filter(court.copul == "court")
nrow(f.mlf.court.f) #17
f.mlf.court.f

f.mlf.copul.f <-fsbLF %>%
  filter(trial_type == "F/MLF") %>%
  filter(mountchoice == "F") %>%
  filter(court.copul == "copul")
nrow(f.mlf.copul.f) #19
f.mlf.copul.f 

#total for females in F/MLF: 36
```
F/MLF Male-like Female
```{r}
f.mlf.court.mlf <-fsbLF %>%
  filter(trial_type == "F/MLF") %>%
  filter(mountchoice == "MLF") %>%
  filter(court.copul == "court")
nrow(f.mlf.court.mlf) #1
f.mlf.court.mlf

f.mlf.copul.mlf <-fsbLF %>%
  filter(trial_type == "F/MLF") %>%
  filter(mountchoice == "MLF") %>%
  filter(court.copul == "copul")
nrow(f.mlf.copul.mlf) #1
f.mlf.copul.mlf 

#total for male-like females in F/MLF: 2
```
M/MLF Male
```{r}
m.mlf.court.m <-fsbLF %>%
  filter(trial_type == "M/MLF") %>%
  filter(mountchoice == "M") %>%
  filter(court.copul == "court")
nrow(m.mlf.court.m) #6
m.mlf.court.m

m.mlf.copul.m <-fsbLF %>%
  filter(trial_type == "M/MLF") %>%
  filter(mountchoice == "M") %>%
  filter(court.copul == "copul")
nrow(m.mlf.copul.m) #13
m.mlf.copul.m

#total for males in M/MLF: 19
```
M/MLF Male-like Female
```{r}
m.mlf.court.mlf <-fsbLF %>%
  filter(trial_type == "M/MLF") %>%
  filter(mountchoice == "MLF") %>%
  filter(court.copul == "court")
nrow(m.mlf.court.mlf) #2
m.mlf.court.mlf

m.mlf.copul.mlf <-fsbLF %>%
  filter(trial_type == "M/MLF") %>%
  filter(mountchoice == "MLF") %>%
  filter(court.copul == "copul")
nrow(m.mlf.copul.mlf) #7
m.mlf.copul.mlf 

#total for male-like females in F/MLF: 9
```
Summary:
M/F: M = 2, F = 25
F/MLF: F = 36, MLF = 2
M/MLF: M = 19, MLF = 9

#How often in M/MLF trials do you see switching from one mount to another within a trial?
```{r}
m.mlf2 <- fsbLF %>%
  filter(trial_type == "M/MLF")

m.mlf2
```
31: MLF to M: 1 M to MLF: 0 Total: 1
58: MLF to M: 0 M to MLF: 0 Total: 0 
67: MLF to M: 2 M to MLF: 1 Total: 3
76: only 1 bout Total: NA/0
79: MLF to M: 1 M to MLF: 1 Total: 2
82: MLF to M: 0 M to MLF: 0 Total: 0
98: MLF to M: 0 M to MLF: 0 Total: 0 

TOTALS: MLF to M: 4 M to MLF: 2 Total:6

#How often in M/MLF trials do you see switching from one mount to another within a bout?
```{r}
m.mlf2 <- fsbLF %>%
  filter(trial_type == "M/MLF")

m.mlf2 #23 unique bouts
```
1: NA         12: NA
2: 0          13: NA
3: 0          14: NA
4: 0          15: NA
5: NA         16: NA
6: 0          17: NA  
7: NA         18: NA
8: NA         19: NA
9: NA         20: NA
10: NA        21: NA
11: NA        22: NA
              23: NA
                                  
NA = only 1 action
Total: 0 switches

#How many cases was sexual behavior followed by agression (overall)
```{r}
total.ag <- fsbLF %>%
  drop_na(aggression_after)

nrow(total.ag) #76 is the output. -2 for "NA neither". So 74.
nrow(fsbLF) #104 total. so 74/104 sex behaviors were followed by aggression
total.ag
```

#How many cases was sexual behavior followed by agression (M/F within bout)
```{r}
#to do this, I'm going to look at the full fsbLF file and will only make note when a bout doesn't have aggression_after
m.f3 <- fsb %>% 
  filter(trial_type == "M/F") %>%
  select(trial_num, bout_num, aggression_after)

m.f3
```
15:1: 0
23:1: 1
23:2: 1
29:1: 1
29:2: 1
29:3: 1
29:4: 1
29:5: 1
36:1: 1
36:2: 1
36:3: 1
38:1: 0
43:1: 1
70:1: 0
70:2: 0
74:1: 1
83:1: 1
93:1: 1
93:2: 1
93:3: 1

total bouts: 20
percent after aggression present: 16/20 (80%)

0 = no aggression after within bout
1 = aggression after within bout

#How many cases was sexual behavior followed by agression (F/MLF within bout)
```{r}
f.mlf3 <- fsb %>%
  filter(trial_type == "F/MLF") %>%
  select(trial_num, bout_num, aggression_after)

f.mlf3
```
16:1: 0
37:1: 0
37:2: 1
47:1: 1
47:2: 1
54:1: 1
54:2: 1
54:3: 0
54:4: 1 
57:1: 0
63:1: 1
72:1: 0
75:1: 1
75:2: 1 
75:3: 1
75:4: 1
75:5: 1
75:6: 1 
75:7: 0
78:1: 1 
78:2: 1
81:1: 0
84:1: 1
84:2: 1
84:3: 1
84:4: 1
84:5: 1 
87:1: 0
94:1: 1
94:2: 0
94:3: 0
94:4: 0
94:5: 0
94:6: 0 

total bouts: 34
% agression: 21/34 (61.7%)

#How many cases was sexual behavior followed by agression (M/MLF within bout)
```{r}
m.mlf3 <- fsb %>%
  filter(trial_type == "M/MLF") %>%
    select(trial_num, bout_num, aggression_after)
 
m.mlf3
```
31:1: 1
31:2: 1
31:3: 1
31:4: 1
31:5: 1
58:1: 0 
67:1: 1
67:2: 1
67:3: 1
67:4: 1
67:5: 1
67:6: 1
67:7: 1
76:1: 1
79:1: 0 
79:2: 0
79:3: 0
79:4: 0
82:1: 1
82:2: 1
98:1: 1
98:2: 1
98:3: 1 

Total bouts: 23
% after agression: 18/23 (78.2%)

##Now lets check within trial
#How many cases was sexual behavior followed by agression (M/F within trial)
```{r}
m.f4 <- fsb %>% 
  filter(trial_type == "M/F") %>%
  select(trial_num, aggression_after)

m.f4
```
15: 0
23: 1
29: 1
36: 1
38: 0
43: 1
70: 0
74: 1
83: 1
93: 1 

total trials: 10
% aggression: 7/10 (70%)

#How many cases was sexual behavior followed by agression (F/MLF within trial)
```{r}
f.mlf4 <- fsb %>%
  filter(trial_type == "F/MLF") %>%
  select(trial_num, aggression_after)

f.mlf4
```
16: 0
37: 1
47: 1
54: 1
57: 0 
63: 1
72: 0 
75: 1
78: 1
81: 0
84: 1
87: 0
94: 1

total bouts: 13
% aggression after: 8/13 (61.5%)

#How many cases was sexual behavior followed by agression (M/MLF within trial)
```{r}
m.mlf4 <- fsb %>%
  filter(trial_type == "M/MLF") %>%
  select(trial_num, aggression_after)

m.mlf4

```
31: 1
58: 0
67: 1
76: 1
79: 0
82: 1
98: 1

total trials: 7
% agression : 5/7 (71.4%)
